Learning Auditory Similarities Between Instrumental Playing Techniques

### 2018-01-29 paper/lagrangeSpontaneousSimilarity2017.tex
addition of analyis code of xp1

The dataset considered in this study is taken
from the studio-on-line (SOL) music library  \cite{peeters2000instrument}.
It has audio recordings of 16 different musical instruments played
with different playing techniques,
which leads to 143 different couples of instrument / playing technique.
For each couple, the pitch and intonation is varied leading to 25444 samples.
The way the dataset is structured
is explained in more details in Appendix \ref{sec:dataset}.

@@

Two music composition professors of the
"conservatoire national sup\'erieur de musique et de danse de Paris", performed the test.
All the couples with a grade higher than three are selected,
bringing 78 \ipts to study.

\vl{This subsection needs a box-and-whisker plot of ratings, where the 143 different
couples of instrument and playing techniques are sorted on the x-axis by average rating. @figure @ratings}

@@

\ml{ok, je regarde si on a toujours les données}

@@

The dataset considered in this paper as been recorded at Ircam and is composed of audio recording of 16 different musical instruments played with different playing techniques, which leads to 143 different couple of instrument / playing technique. For each couple, the pitch and intonation is varied leading to 25444 audio samples.

>>>>

The dataset considered in this study is taken
from the studio-on-line (SOL) music library  \cite{peeters2000instrument}.
It has audio recordings of 16 different musical instruments played
with different playing techniques,
which leads to 235 different couples of instrument / playing technique.
For each couple, the pitch and intonation is varied leading to 25444 samples.
The way the dataset is structured
is explained in more details in Appendix \ref{sec:dataset}.

@@

Two music composition professors of the
"conservatoire national sup\'erieur de musique et de danse de Paris" performed the test.
All the couples with a grade higher than three are selected,
bringing 78 \ipts to study.

\vl{This subsection needs a box-and-whisker plot of ratings, where the 235 different
couples of instrument and playing techniques are sorted on the x-axis by average rating. @figure @ratings}

@@

\ml{les histograms sont dans la figure statxp1. Le code pour la generer est dans code/xp1 faire tourner extractData et statData. Un ttest ne rejette pas l'hypothese nulle.}

@@

The dataset considered in this paper as been recorded at Ircam and is composed of audio recording of 16 different musical instruments played with different playing techniques, which leads to 235 different couple of instrument / playing technique. For each couple, the pitch and intonation is varied leading to 25444 audio samples.
